### 2014-10-17 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
Reports: Additional minor edits
San Francisco: Add figures of temperature slices in garage to Assessing the Hazard section

>>>>

The hot gases in the flow path were exiting the structure from the garage door and front door, as shown in Fig.~\ref{fig:flow_path_top}. From the NIOSH report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows temperature contours in the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.

\begin{figure}[!ht]
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_340_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_352_s}
\input{../Figures/colorbar_metric_temp}
\input{../Figures/colorbar_std_temp}
\caption[Simulated temperature contours in the garage after basement window failure.]
{Top view of simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
\label{fig:smv_flow_path_garage}
\end{figure}

In Fig.~\ref{fig:smv_flow_path_garage}, the first snapshot is shown at a simulation time of 340~s, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a simulation time of 352~s, which is 10~s after the first rear basement window failed. Before the rear basement window failed, the temperature of the gases exiting the garage door were less than 150~$^{\circ}$C (300~$^{\circ}$F). After the rear basement window failed, the temperature of the gases exiting the garage door were in excess of 430~$^{\circ}$C (800~$^{\circ}$F).
